---
title: "MI Research Survey"
author: "William Hope"
date: "2023-10-27"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plm)
library(AER)
library(stargazer)
library(ggplot2)
library(stats)
library(gplots)
library(combinat)
library(car)
library(mediation)
```

# Setting the working directory
```{r}
# Read the CSV file and store it in a data frame
data <- read.csv("IceCool_MI.csv")

# View the first few rows of the data frame
head(data)

```

# Summary Stats and Distribution

## Q1 - Consumption
```{r}
# Analysis Related to Consumption Variable

summary(data$consumption)

## This histogram shows the distribution for values for question 1 data, it relates to the consumption
hist(data$consumption, 
     main = "Distribution of consumption variable",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```



## Q2 - consumption_reason
```{r}
# Analysis Related to consumption_reason Variable

summary(data$consumption_reason)

## This histogram shows the distribution for values for question 2 data, it relates to the consumption_reason reasons
hist(data$consumption_reason, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```



## Q3 - brand_frequency
```{r}
# Analysis Related to brand_frequency Variable

summary(data$brand_frequency)


# This histogram shows the distribution for values for question 3 data, it relates to the brand_frequency
hist(data$brand_frequency, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```

## Q4 - brand_switching
```{r}
# Analysis Related to brand_switching Variable

## Flitering out the "No Usual Brand" answers for more accurate results
filtered_brand_switching <- data$brand_switching[data$brand_switching != 0]

summary(filtered_brand_switching)

# This histogram shows the distribution for values for question 4 data, it relates to the brand_switching
hist(filtered_brand_switching, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(filtered_brand_switching, mu = 3, alternative = "less")
t.test(filtered_brand_switching, mu = 3, alternative = "greater")

```


## Q5 - usual_brand
```{r}
# Analysis Related to usual_brand Variable

summary(data$usual_brand)

# This histogram shows the distribution for values for question 3 data, it relates to the usual_brand
hist(data$usual_brand, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```


## Q6 - price_importantce
```{r}
# Analysis Related to price Variable

summary(data$price_importantce)

# This histogram shows the distribution for values for question 3 data, it relates to the price
hist(data$price_importantce, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$price_importantce, mu = 3, alternative = "less")
t.test(data$price_importantce, mu = 3, alternative = "greater")
t.test(data$price_importantce, mu = 3)

```

It is clear gender does not play a role in the price importance. It is also relevant to suggest that discounts play a huge importance to price importance. This means as price sensitivity increases, discount importance also increases.

## Q7 - discount_importance
```{r}
# Analysis Related to discount Variable

summary(data$discount_importance)

# This histogram shows the distribution for values for question 3 data, it relates to the brand_frequency
hist(data$discount_importance, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$discount_importance, mu = 3, alternative = "less")
t.test(data$discount_importance, mu = 3, alternative = "greater")
t.test(data$discount_importance, mu = 3)

```



## Q8 - stu_price_sense
```{r}
# Analysis Related to stu_price_sense Variable

## Flitering out the "Unsure" answers for more accurate results
filtered_stu_price_sense <- data$stu_price_sense[data$stu_price_sense != 2]

summary(data$filtered_stu_price_sense)
summary(data$stu_price_sense)
summary(filtered_stu_price_sense)

hist(filtered_stu_price_sense, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$filtered_stu_price_sense, mu = 1)
t.test(data$filtered_stu_price_sense, mu = 0)

```



## Q9 - first_hear
```{r}
# Analysis Related to first_hear Variable

summary(data$first_hear)

hist(data$first_hear, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)
```



## Q10 - familiarity
```{r}
# Analysis Related to familiarity Variable

summary(data$filtered_familiarity)

hist(data$filtered_familiarity, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$filtered_familiarity, mu = 0, alternative = "greater")
t.test(data$filtered_familiarity, mu = 1)
t.test(data$filtered_familiarity, mu = 0)
```



## Q11 - marketing
```{r}
# Analysis Related to marketing Variable

filtered_marketing <- data$marketing[data$marketing != 2]

summary(filtered_marketing)

hist(filtered_marketing, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(filtered_marketing, mu = 1)
t.test(filtered_marketing, mu = 1, alternative = "less")
t.test(filtered_marketing, mu = 0)


```



## Q12 - influence_marketing
```{r}
# Analysis Related to influence_marketing Variable

summary(data$influence_marketing)

hist(data$influence_marketing, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$influence_marketing, mu = 3, alternative = "less")
t.test(data$influence_marketing, mu = 3, alternative = "greater")
t.test(data$influence_marketing, mu = 3)

```



## Q13 - package_design
```{r}
# Analysis Related to package_design Variable

summary(data$package_design)

hist(data$package_design, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$package_design, mu = 3, alternative = "less")
t.test(data$package_design, mu = 3, alternative = "greater")
t.test(data$package_design, mu = 3)


```



## Q14 - visua_appeal
```{r}
# Analysis Related to visua_appeal Variable

summary(data$visua_appeal)

hist(data$visua_appeal, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$visua_appeal, mu = 3, alternative = "less")
t.test(data$visua_appeal, mu = 3, alternative = "greater")
t.test(data$visua_appeal, mu = 3)

```



## Q15 - info_packaging
```{r}
# Analysis Related to info_packaging Variable

summary(data$info_packaging)

hist(data$info_packaging, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$info_packaging, mu = 3, alternative = "less")
t.test(data$info_packaging, mu = 3, alternative = "greater")
t.test(data$info_packaging, mu = 3)


```



## Q16 - sweetness
```{r}
# Analysis Related to sweetness Variable

filtered_sweetness <- data$sweetness[data$sweetness != 0]

summary(data$sweetness)

hist(filtered_sweetness, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(filtered_sweetness, mu = 3, alternative = "less")
t.test(filtered_sweetness, mu = 3, alternative = "greater")
t.test(filtered_sweetness, mu = 3)


```



## Q17 - natural_ingre
```{r}
# Analysis Related to natural_ingre Variable

summary(data$natural_ingre)

hist(data$natural_ingre, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$natural_ingre, mu = 3, alternative = "less")
t.test(data$natural_ingre, mu = 3, alternative = "greater")
t.test(data$natural_ingre, mu = 3)


```



## Q18 - with_coconut
```{r}
# Analysis Related to with_coconut Variable

summary(data$with_coconut)

hist(data$with_coconut, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(data$with_coconut, mu = 2, alternative = "less")
t.test(data$with_coconut, mu = 2, alternative = "greater")
t.test(data$with_coconut, mu = 2)

```



## Q20 - unique_values
```{r}
# Analysis Related to unique_values Variable

filtered_unique_values <- data$unique_values[data$unique_values != 2]

summary(data$filtered_unique_values)

hist(data$filtered_unique_values, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

t.test(filtered_unique_values, mu = 1)
t.test(filtered_unique_values, mu = 0)
t.test(filtered_unique_values, mu = 1, alternative = "less")
t.test(filtered_unique_values, mu = 1, alternative = "greater")


```



## Q22 - age
```{r}
# Analysis Related to age Variable

summary(data$age)

hist(data$age, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```



## Q23 - gender
```{r}
# Analysis Related to gender Variable

summary(data$gender)

hist(data$gender, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)


```

## Q24 - occupation
```{r}
# Analysis Related to occupation Variable

summary(data$occupation)

hist(data$occupation, 
     main = "Distribution of Values",
     xlab = "Value",
     ylab = "Frequency",
     col = "lightblue",
     border = "black",
     breaks = 5)

```

## Regression Analysis Among Variables
```{r}
# Influential Marketing Regressions
fit1 <- lm(data$influence_marketing ~ data$filtered_marketing, data=data)
               se_fit1 <- sqrt(diag(vcovHC(fit1)))
               
fit2 <- lm(data$influence_marketing ~ data$price_importantce + data$gender, data=data)
               se_fit2 <- sqrt(diag(vcovHC(fit2)))
               
fit3 <- lm(data$influence_marketing ~ data$price_importantce + data$gender + data$filtered_unique_values, data=data)
               se_fit3 <- sqrt(diag(vcovHC(fit3)))

fit4 <- lm(data$influence_marketing ~ data$discount_importance + data$gender + data$filtered_unique_values, data=data)
               se_fit4 <- sqrt(diag(vcovHC(fit4)))
               
stargazer(fit1, fit2, fit3, fit4, se=list(se_fit1, se_fit2, se_fit3, se_fit4), header=FALSE, float=FALSE, type = "text", digits=4, model.numbers=FALSE)

stargazer(fit3, fit4, se=list(se_fit3, se_fit4), header=FALSE, float=FALSE, type = "text", digits=4, model.numbers=FALSE)

```


```{r}
# Packaging Variables Regression Models
fit_pack <- lm(data$package_design~data$gender, data=data)
se1_fit_pack <- sqrt(diag(vcovHC(fit_pack)))

fit_pack2 <- lm(data$info_packaging~data$brand_switching+data$consumption_reason, data=data)
se1_fit_pack2 <- sqrt(diag(vcovHC(fit_pack2)))

fit_pack3 <- lm(data$visua_appeal~data$brand_switching+data$age, data=data)
se1_fit_pack3 <- sqrt(diag(vcovHC(fit_pack3)))

stargazer(fit_pack, fit_pack2, fit_pack3, se=list(se1_fit_pack, se1_fit_pack2, se1_fit_pack3), header=FALSE, float=FALSE, type = "text", digits=4, model.numbers=FALSE)

```


```{r}
# Regressing Price_sense against Brand_Aware, Packaging, and Taste
fit_price_sense <- lm(data$price_sense~data$brand_aware+data$packaging+data$taste, data=data)
se1_fit_price_sense <- sqrt(diag(vcovHC(fit_price_sense)))

# Regressing Price_sense against Brand_Aware, Packaging, and Gender
fit_gender_price <- lm(data$price_sense~data$brand_aware+data$packaging+data$gender, data=data)
se1_fit_gender_price <- sqrt(diag(vcovHC(fit_gender_price)))

# Regressing Price_sense against Brand_Aware, Packaging, Gender, Age
fit_apgi <- lm(data$price_sense~data$brand_aware+data$packaging+data$gender+data$age, data=data)
se1_fit_apgi <- sqrt(diag(vcovHC(fit_apgi)))

# Displaying Regression Results
stargazer(fit_price_sense, fit_gender_price, fit_apgi, se=list(se1_fit_price_sense, se1_fit_gender_price, se1_fit_apgi), header=FALSE, float=FALSE, type = "text", digits=4, model.numbers=FALSE)
```


```{r}

# Get the names of numeric variables
numeric_vars <- names(data)[sapply(data, is.numeric)]

# Create a list to store correlation results
correlation_results <- list()

# Loop through all unique combinations of variables and calculate correlations
for (i in 1:(length(numeric_vars) - 1)) {
  for (j in (i + 1):length(numeric_vars)) {
    var1 <- numeric_vars[i]
    var2 <- numeric_vars[j]
    
    # Calculate the correlation for the pair of variables
    correlation_result <- cor(data[[var1]], data[[var2]], use = "pairwise.complete.obs")
    
    # Store the correlation result
    correlation_results[[paste(var1, var2, sep = "_")]] <- correlation_result
  }
}

# Print strong positive correlation results (magnitudes between 0.7 and 0.9)
for (var_pair in names(correlation_results)) {
  correlation_value <- correlation_results[[var_pair]]
  if (!is.na(correlation_value) && abs(correlation_value) >= 0.6 && abs(correlation_value) <= 0.99) {
    cat("Strong correlation between", var_pair, "is", correlation_value, "\n")
  }
}

# Print moderate positive correlation results (magnitudes between 0.5 and 0.7)
for (var_pair in names(correlation_results)) {
  correlation_value <- correlation_results[[var_pair]]
  if (!is.na(correlation_value) && abs(correlation_value) >= 0.31 && abs(correlation_value) <= 0.59) {
    cat("Moderate correlation between", var_pair, "is", correlation_value, "\n")
  }
}

# Print weak positive correlation results (magnitudes between 0.2 and 0.49)
for (var_pair in names(correlation_results)) {
  correlation_value <- correlation_results[[var_pair]]
  if (!is.na(correlation_value) && abs(correlation_value) >= 0 && abs(correlation_value) <= 0.24) {
    cat("Weak correlation between", var_pair, "is", correlation_value, "\n")
  }
}


```


# Testing for Multicollinearity
```{r}

# Calculate VIF for the model
vif_results <- vif(fit_gender_price)
vif_results

# Calculate tolerance
tolerance <- 1 / vif_results
tolerance

# Create a correlation matrix for predictor variables
cor_matrix <- cor(data[, c("age", "gender", "packaging")])

# Calculate eigenvalues
eigenvalues <- eigen(cor_matrix)$values
eigenvalues

# Perform PCA on predictor variables
pca_result <- prcomp(data[, c("age", "gender", "packaging")])
summary(pca_result)

# Mediation Analysis

model <- lm(price_sense ~ packaging + age + gender, data = data)
mediator_model <- lm(packaging ~ price_sense + age + gender, data = data)
mediation_result <- mediate(model, mediator_model, treat = "price_sense", mediator = "packaging", control = c("age", "gender"))
summary(mediation_result)


```
